---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# codex

<!-- badges: start -->
<!-- badges: end -->

Datasets for teaching quantitative approaches and modeling in archaeology and paleontology. This package provides several types of data, relating to typologies, diversity measurement, cultural evolution, radiocarbon dating and paleoenvironments.

When using **codex**, you must cite the relevant publications for each dataset (see the documentation).

## Installation

You can install the released version of **codex** from [CRAN](https://CRAN.R-project.org) with:

```{r cran-installation, eval=FALSE}
install.packages("codex")
```

And the development version from [GitHub](https://github.com/) with:

```{r gh-installation, eval=FALSE}
# install.packages("remotes")
remotes::install_github("tesselle/codex")
```

## Contributing
Please note that the **codex** project is released with a [Contributor Code of Conduct](https://github.com/tesselle/codex/blob/master/.github/CODE_OF_CONDUCT.md). By contributing to this project, you agree to abide by its terms.
